# Reproducible Research: Peer Assessment 1
### by Adriana Rivera






## Loading and preprocessing the data
```{r}
myActivity <- read.csv("activity.csv")

```


## What is mean total number of steps taken per day?
#### First we want to see the total number of steps taken each day during 2 months
```{r}
require(ggplot2) #need to quiet to output for this one.
```

```{r}

qplot(date, data=myActivity, weight= steps, geom="histogram")
```

#### Now we calculate the mean and median of steps taken per day
```{r}

mySums <- by(myActivity[,1], myActivity$date, sum) #this are the total number of steps per day.
mean(mySums, na.rm = TRUE)
median(mySums, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r}
#fIntervals <- factor(myActivity[,3])
myIntervalMean <- aggregate(myActivity$steps, list(Interval = myActivity$interval), mean, na.rm=TRUE) #this are the total number of steps per day.
qplot(myIntervalMean$Interval, myIntervalMean$x, geom = "line")
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
  